---
title: "P8105_HW_sm5567"
author: Shina Min
date: September 2023
output:
  github_document:
    toc: true
---


# Section 1

* The variables in this dataset: 15 variables including origin, year, month, day, hour, temp, dewp, humid, wind_dir, wind_speed, wind_qust, precip, pressure, visib, and time_hour. 

* This dataset has 358 entries. 

* The dataset has `r nrow ("early_january_weather")` 15 rows and
`r ncol("early_january_weather")` 358 columns.

* The mean of temperature is 39.58212


```{r}

library(ggplot2)
library(moderndive)
library(tidyverse)
data("early_january_weather")

n_rows <- nrow(early_january_weather)
n_cols <- ncol(early_january_weather)

mean_temp <- mean(early_january_weather$temp) 
mean(pull(early_january_weather,'temp'))
     
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + 
  geom_point() + labs(x = "Time Hour", y = "Temperature", color = "Humidity")

ggsave("Shinaplot.pdf",plot = last_plot())

```


# Section 2

* Data frame comprised of: 

```{r s2_df_create}
samp = rnorm(10)
length(samp)

s2_df = tibble(
  samp = rnorm(10, sd = 1),
  vec_logical = samp > 0,
  vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i","j"),
  vec_factor = factor(c("red", "green", "blue","red", "green", "blue", "red","green","blue", "red"))
)
```


```{r s2_df_mean}

library(tidyverse)
mean_samp = pull(s2_df, samp)
mean_vec_logical = pull(s2_df, vec_logical)
mean_vec_char = pull(s2_df, vec_char)
mean_vec_factor = pull(s2_df, vec_factor)

```


* Calculating the mean of the numeric vector (mean_numeric) works fine because it contains numeric values.
* Calculating the mean of the logical vector (mean_logical) also works, as R can treat TRUE as 1 and FALSE as 0, so it calculates the mean correctly.
* However, attempting to calculate the mean of the character vector (mean_character) and the factor vector (mean_factor) results in an error because you cannot calculate the mean of non-numeric or factor variables directly.


```{r s2_df_apply}

as.numeric(pull(s2_df, samp))
as.numeric(pull(s2_df, vec_logical))
as.numeric(pull(s2_df, vec_char))
as.numeric(pull(s2_df, vec_factor))

```

* "NAs introduced by coercion" happened because R is trying to convert non-numeric values (characters) to a numeric data type using the as.numeric function.
* Other codes worked because they have numeric values. 
* In summary, whether it makes sense to calculate the mean depends on what your data represents. For "yes" or "no" data, it works. For words, it doesn't make sense. For categories, you can do it, but the result might not mean anything useful in practice.


